The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2020-12-02 Manuscript/manuscript.tex
Update manuscript.tex

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{NBABubbleAnalysis_files/figure-latex/Fig1-1}
  \caption{Winning percentage of NBA home teams in the playoffs since
    2010, the green line denotes .500.}
  \label{fig:Fig1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{NBABubbleAnalysis_files/figure-latex/Fig2-1}
  \caption{Histograms of home (blue) and away (red) scoring
    for 2020 (bottom) and 2017-2019 (top).}
  \label{fig:Fig2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{NBABubbleAnalysis_files/figure-latex/Fig3-1}
  \caption{Histograms of home shooting percentages for two-
    pointers, three-pointers and free throws for 2020 (top) vs.~2017-19
    (bottom).}
  \label{fig:Fig3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{NBABubbleAnalysis_files/figure-latex/Fig4-1}
  \caption{Histograms of away shooting percentages for two-pointers,
    three-pointers and free throws for 2020 (top) vs.~2017-19
    (bottom).}
  \label{fig:Fig4}  
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{Fig1}
  \caption{Winning percentage of NBA home teams in the playoffs since
    2010, the green line denotes .500.}
  \label{fig:Fig1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{Fig2}
  \caption{Histograms of home (blue) and away (red) scoring
    for 2020 (bottom) and 2017-2019 (top).}
  \label{fig:Fig2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{Fig3}
  \caption{Histograms of home shooting percentages for two-
    pointers, three-pointers and free throws for 2020 (top) vs.~2017-19
    (bottom).}
  \label{fig:Fig3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{Fig4}
  \caption{Histograms of away shooting percentages for two-pointers,
    three-pointers and free throws for 2020 (top) vs.~2017-19
    (bottom).}
  \label{fig:Fig4}  
\end{figure}
